\thesistitle

### 2019-08-02 sections/background.tex
Finished refactorability

\subsection{AST}
An Abstract Syntax Tree (AST) is a tree consisting of an hierarchical representation of the source code of a program. Detecting code clones on the AST of a program allows for a deeper understanding of the concepts that are being analyzed. Having an AST, we know how concepts in the code are related. This helps to determine in what classes and methods cloned code is found.

@@

The AST consists of nodes of the following types (examples are for Java):
\begin{itemize}
  \item \textbf{Declarations}: Method-declaration, class-declaration, etc.
  \item \textbf{Statements}: If-statement, switch-statement, expression-statement, etc.
  \item \textbf{Expressions}: Variables, literals, method calls, variable assignments, etc.
  \item \textbf{Types}: Primitives, reference types, void, etc.
\end{itemize}

>>>>

\subsection{AST} \label{sec:astbackground}
An Abstract Syntax Tree (AST) is a tree consisting of an hierarchical representation of the source code of a program. Detecting code clones on the AST of a program allows for a deeper understanding of the concepts that are being analyzed. Having an AST, we know how concepts in the code are related. This helps to determine in what classes and methods cloned code is found.

@@

The AST consists of nodes of the following types (examples are for Java):
\begin{itemize}
  \item \textbf{Declarations}: Method-declaration, class-declaration, etc.
  \item \textbf{Statements}: If-statement, switch-statement, expression-statement, etc.
  \item \textbf{Expressions}: Variables, literals, method calls, variable assignments, etc.
  \item \textbf{Types}: Primitives, reference types, void, etc.
  \item \textbf{Clauses}: Catch-clause, else-clause, etc.
\end{itemize}

### 2019-08-02 sections/clonerefactor.tex
Finished refactorability

\subsubsection{Is Not A Partial Method}
The ``Extract Method'' refactoring can only refactor code in the body of a method. We mapped the contents of clones in section \ref{sec:setuplocation}. Here we defined the ``Partial Method'' catagory as \textit{a clone that spans (a part of) the body of a method. The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is probably not the correct technique for refactoring such clones.

\todo{Finish this section}

@@

\subsection{Saving refactored code}
CloneRefactor features several ``Refactoring Strategies'', that indicate how and where refactored code will be saved. These are as follows:
\begin{itemize}
  \item \textbf{Do not refactor}: CloneRefactor does not apply refactorings at all, it only reports found clones.
  \item \textbf{Replace}: CloneRefactor replaces the source code with the refactored source code.
  \item \textbf{Copy Only Changes}: CloneRefactor writes only the changed files to a new location.
  \item \textbf{Copy All}: CloneRefactor copies the entire project to a new location and applies the refactorings there. This makes sure the original project stays unmodified, while also having a snapshot of the refactored project.
  \item \textbf{Git Replace}: CloneRefactor creates a branch on the git VCS, or initializes a git repository if it is not available. For every clone class refactored, CloneRefactor creates a commit in the git repository.
  \item \textbf{Git Copy}: CloneRefactor copies the entire project to a new location. CloneRefactor then performs the same procedure as for ``Git Replace'', except now at the new location so the original project remains unmodified.
\end{itemize}

>>>>

\subsubsection{Is Not A Partial Method}
The ``Extract Method'' refactoring can only refactor code in the body of a method. We mapped the contents of clones in section \ref{sec:setuplocation}. Here we defined the ``Partial Method'' catagory as \textit{a clone that spans (a part of) the body of a method. The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is likely not to be correct technique for refactoring such clones.

\subsubsection{Top-level Node Is Not A Statement}
A method body can only consist of statements. We cannot put declarations in a method. However, there are possibilities where a clone consists of something else than a statement as top level node. The most prominent example is when a clause is cloned (see section \ref{sec:astbackground} for examples of such concepts). For instance, we cannot extract only the catch-clause of a try-statement to a new method. In such a case, we should either extract the complete try-statement, or only the contents of the catch clause.

\subsubsection{Overlaps}
We do not consider clone classes for refactoring that overlap in the clone class itself. That is because such clones may require other techniques to refactor them. We consider analyzing such refactoring methods future work. An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}. In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}. To refactor such clones, other techniques may be required, like introducing a new for-loop to reduce the duplication.

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
// Original
public void sayHello(){
|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring1}|
|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring2}|
|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring3}|
|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring4}|
|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring5}|
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// Refactored
public void sayHello(){
|\highlightYellow|  for(int i = 0; i<5; i++){
|\highlightYellow|    System.out.println("hello!");
|\highlightYellow|  }
}
\end{javacode}}
\end{parcolumns}
\caption{Refactoring a clone class that has overlap between clone instances.}
\label{fig:overlaprefactoring}
\end{figure}

\subsubsection{Can be extracted}
All clones that do not adhere to any of above-stated categories, are considered suitable for method extraction.

@@

\subsection{Saving refactored code}
CloneRefactor features several ``Refactoring Strategies'', that indicate how and where refactored code will be saved. These are as follows:
\begin{itemize}
  \item \textbf{Do not refactor}: CloneRefactor does not apply refactorings at all, it only reports found clones.
  \item \textbf{Simulate}: CloneRefactor only applies the refactorings to its internal AST structure and calculates the results of applying these refactorings. It does not modify/copy the codebase on disk.
  \item \textbf{Replace}: CloneRefactor replaces the source code with the refactored source code.
  \item \textbf{Copy Only Changes}: CloneRefactor writes only the changed files to a new location.
  \item \textbf{Copy All}: CloneRefactor copies the entire project to a new location and applies the refactorings there. This makes sure the original project stays unmodified, while also having a snapshot of the refactored project.
  \item \textbf{Git Replace}: CloneRefactor creates a branch on the git VCS, or initializes a git repository if it is not available. For every clone class refactored, CloneRefactor creates a commit in the git repository.
  \item \textbf{Git Copy}: CloneRefactor copies the entire project to a new location. CloneRefactor then performs the same procedure as for ``Git Replace'', except now at the new location so the original project remains unmodified.
\end{itemize}
